Analyzing Performance Bottleneck in Graph Neural Network Training: An Experimental View

### 2020-07-15 Manuscript/sec6-related-work.tex
update初稿

\subsection{GNNs survey}
GNNs survey: Zhou et al \cite{zhou2018_gnn_review}, Zhang et al \cite{zhou2018_gnn_review} and Wu et al \cite{comprehensive-survey-wu-2020} 
surveyed existing graph neural works models in different categorizations and viewpoints and provided a comprehensive review about GNNs' model 
architecture, principle and application. Dwived et al \cite{dwivedi2020_benchmark_of_gnn} discussed the performance of different GNN algorithms 
under the graph dataset of different scenes, and gived the key operators of designing effective GNNs in different scenarios. 
However, these efforts are focused on the GNN algorithm itself and accuracy, without a detailed analysis of memory usage and running time.

>>>>

\subsection{GNNs survey}
Zhou et al \cite{zhou2018_gnn_review}, Zhang et al \cite{zhang2018_gnn_survey} and Wu et al \cite{comprehensive-survey-wu-2020} 
surveyed existing graph neural works models in different categorizations and viewpoints and provided a comprehensive review about GNNs' model 
architecture, principle and application. Dwived et al \cite{dwivedi2020_benchmark_of_gnn} discussed the performance of different GNN algorithms 
under the graph dataset of different scenes, and gived the key operators of designing effective GNNs in different scenarios. 
However, these efforts are focused on the GNN algorithm itself and accuracy, without a detailed analysis of memory usage and running time.
